Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-10 document/ms.tex
sweeping things under the rug

The constraints in \eq{crazypost} can always be---and often are---propagated
as a list of $N$ samples $\{\entry_k^{(n)}\}$ from the posterior
\begin{eqnarray}
\entry_k^{(n)} &\sim& p(\{\entry_k\}\,|\,\{\data_k\},\,\interim) \quad.
\end{eqnarray}
We can use these samples to approximately compute the integral in
\eq{simplemarglike} as
\begin{eqnarray}
\frac{p(\{\data_k\}\,|\,\ratepars)}{p(\{\data_k\}\,|\,\interim)} &\approx&
    \frac{1}{N} \sum_{n=1}^N
    \frac{p(\{\entry_k^{(n)}\}\,|\,\ratepars)}
         {p(\{\entry_k^{(n)}\}\,|\,\interim)} \quad.
\end{eqnarray}
This is very efficient to compute as long as an evaluation of
$p(\{\entry_k^{(n)}\}\,|\,\ratepars)$ is not very expensive.
That being said, this could be a high variance estimator depending on the
initial choice of $p(\{\entry_k^{(n)}\}\,|\,\interim)$ but in our case, we'll
show that not many samples are needed to get an accurate estimate.

@@

Using an independent exoplanet search and characterization pipeline,
\citet{petigura} published a catalog of 603 planet candidates orbiting stars
in their ``Sun-like'' sample of \kepler\ targets.
For each candidate, \citet{petigura} used Markov chain Monte Carlo to sample
the posterior probability density---presumably assuming uniform priors---for
the radius ratio, transit duration, and impact parameter.
They then incorporated the uncertainties in the stellar radius and published
constraints on the physical radii of their candidates.
The exact shape of the implied prior on planet radius depends on the assumed
priors on radius ratio and stellar radius but in the limit of a broad uniform
prior on each quantity, the implicit prior at small physical radius is
approximately uniform; this is the assumption that we make.

@@

Given our domain knowledge of how detection efficiency depends on the physical
parameters, it might seem silly to measure the survey completeness in period
and radius instead of radius ratio or signal-to-noise.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
The main argument is that since the radius uncertainties are dominated by
uncertainties in the stellar parameters, it is not possible to use the
published catalog (\citealt{petigura}) to compute constraints on radius
ratios.
In future catalogs, this problem would be solved by publishing representations
of the posterior probabilities that are being measured.
In this case, these parameters are radius ratio and stellar radius instead of
just the physical radius.

>>>>

The constraints in \eq{crazypost} can always be---and often are---propagated
as a list of $N$ samples $\{\entry_k^{(n)}\}$ from the posterior
\begin{eqnarray}
\entry_k^{(n)} &\sim& p(\{\entry_k\}\,|\,\{\data_k\},\,\interim) \quad.
\end{eqnarray}
We can use these samples to approximately compute the integral in
\eq{simplemarglike} as
\begin{eqnarray}\eqlabel{importance}
\frac{p(\{\data_k\}\,|\,\ratepars)}{p(\{\data_k\}\,|\,\interim)} &\approx&
    \frac{1}{N} \sum_{n=1}^N
    \frac{p(\{\entry_k^{(n)}\}\,|\,\ratepars)}
         {p(\{\entry_k^{(n)}\}\,|\,\interim)} \quad.
\end{eqnarray}
This is very efficient to compute as long as an evaluation of
$p(\{\entry_k^{(n)}\}\,|\,\ratepars)$ is not very expensive.
That being said, this could be a high variance estimator depending on the
initial choice of $p(\{\entry_k^{(n)}\}\,|\,\interim)$ but in our case, we'll
show that not many samples are needed to get an accurate estimate.

@@

Using an independent exoplanet search and characterization pipeline,
\citet{petigura} published a catalog of 603 planet candidates orbiting stars
in their ``Sun-like'' sample of \kepler\ targets.
For each candidate, \citet{petigura} used Markov chain Monte Carlo to sample
the posterior probability density---presumably assuming uniform priors---for
the radius ratio, transit duration, and impact parameter.
They then incorporated the uncertainties in the stellar radius and published
constraints on the physical radii of their candidates.
Given this data reduction and since we don't have access to the individual
posterior constraints on radius ratio and stellar radius, we can't directly
compute the importance weights $p(\{\entry_k^\}\,|\,\interim)$ needed for
\eq{importance}.
For the rest of this \paper, we'll make the simplifying assumption that these
weights are constant in log-period and log-radius but the results don't seem
to be sensitive to this specific choice.

@@

Given our domain knowledge of how detection efficiency depends on the physical
parameters, it might seem silly to measure the survey completeness in period
and radius instead of radius ratio or signal-to-noise.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
The main argument is that since the radius uncertainties are dominated by
uncertainties in the stellar parameters, it is not possible to use the
published catalog (\citealt{petigura}) to compute constraints on radius
ratios.
In future catalogs, this problem would be solved by publishing representations
of all the posterior probabilities that are being measured.
In this case, the most useful data product would be \emph{posterior samples
for each target's radius ratio and stellar radius}.
